\TheTitle

### 2016-07-25 linvis.tex
Updated the text of the paper with the explanation of the evaluation.
I also trimmed the paper to 10 pages by playing a bit with the spacing.

@@

\begin{figure*}
        \centering
        \includegraphics[width=0.97\textwidth]{figures/gitk.png}
        \caption{A view of the Gitk interface centered on merge
          b34870fc9ff15fe46c4066faeeec437a4e63e2d8 by Miller. Commits point toward
          their ancestors and there is no clear path from the commit to the merge
          with the master branch. Neither Gitk nor Git are capable of showing the
          commits in master.}
        \label{fig:gitk}
\end{figure*}

\begin{figure}
        \centering
        \includegraphics[width=0.45\textwidth]{figures/github_viewer.png}
        \caption{Github Failure Message showing the DAG of the Linux Project and its
                relationship to other forks.}
        \label{fig:gitfail}
\end{figure}

@@

        \foreach \x in {0, 1, 2, 3, 4, 5, 6, 7, 8}
    \node[shift={(\x, -0.6)}, color=black] {$t_\x$};
  \end{tikzpicture}
  \caption{Example of a sequence of events performed in different
    repositories. The horizontal axis represents time. Each horizontal
    section represents a different branch and/or repository. Each commit
    points to its ancestor.}
  \label{fig:repoEvents}
\end{figure}

@@

    \draw (12) edge[-stealth] (11) edge[chartyellow, -stealth] (10);
    \draw (11) edge[-stealth] (4) edge[chartyellow, -stealth] (9);
    \draw (10) edge[chartyellow, -stealth] (9);
    \draw (9) edge[chartmagenta, -stealth] (8) edge[chartred, -stealth] (6)
              edge[chartyellow, -stealth] (7);
    \draw (8) edge[chartmagenta, -stealth] (7);
    \draw (7) edge[chartyellow, -stealth] (5);
    \draw (6) edge[chartred, -stealth] (5);
    \draw (5) edge[chartmagenta, -stealth] (3) edge[chartyellow,-stealth] (2)
              edge[chartyellow, -stealth] (4);
    \draw (4) edge[-stealth] (1);
    \draw (3) edge[chartmagenta, -stealth] (2);
    \draw (2) edge[chartyellow, -stealth] (1);
  \end{tikzpicture}
  \caption{DAG representation of the commits represented in
    Figure~\ref{fig:repoEvents}. The DAG loses information about which
    repository the commit is performed in and through which merges it
    has passed on its way to the master branch. The DAG does not even
    distinguish the master branch from other branches.}
  \label{fig:repoDAG}
\end{figure}

@@

  \end{tikzpicture}
  \caption{Merge-tree view of the commits  represented in
    Figure~\ref{fig:repoEvents} showing the path they followed to reach
    the master branch. In this model the successors of each commit
    represents the path followed by that commit to reach the master
    branch.}
  \label{fig:repoTree}
\end{figure}

@@

\begin{algorithm}
        \caption{Computing the merge-tree of Linux Git's DAG}\label{fig:alg}
        \begin{algorithmic}
                \Function{ComputeMergeTree}{DAG}: tree
                \State {\# Compute the tree from the DAG of Linux repository.}
                \State {\# Returns $Tree$, a graph containing every commit }
                \State {\# in DAG with the path it followed to master.\\}

@@

* 'for-linus' of git://neil.brown.name/md: (24 commits)
md: clean up do_md_stop
[... edited for the sake of space]
md: split out md_rdev_init
md: be more careful setting MD_CHANGE_CLEAN
md/raid5: ensure we create a unique name for kmem_cache...
...
        \end{verbatim}}
        \caption{Example of how merges record a subset of commits being merged. The
                commit only shows the first 20 one-line log messages for the 24
                non-merge commits it merged. The ending ``...'' is part of the log
                and represents that other commits were merged.}
        \label{fig:sampleMerge}
\end{figure}

\textbf{rewrite}

We use this information to evaluate the accuracy of the merge-tree model extracted
from the DAG. For commits with no conflicts, we compare: 1) the number of non-merge
commits, 2) the summaries of the commits available in the log, and 3) the summaries
of the merges included.

The verification detected no incorrect merges since 2013, two incorrect merges in
2012, and two in 2011; however, the heuristic breaks in October, 15, 2009 due to the
presence of \textit{foxtrot} commits, which confounds the true master branch of a
repository
\footnote{See \url{http://bit-booster.blogspot.ca/2016/02/no-foxtrots-allowed.html} for a description of the issue}, and will not work for older merges.

>>>>

\begin{figure*}
        \centering
        \includegraphics[width=0.97\textwidth]{figures/gitk.png}
        \caption{A view of the Gitk interface centered on merge
          b34870fc9ff15fe46c4066faeeec437a4e63e2d8 by Miller. Commits point toward
          their ancestors and there is no clear path from the commit to the merge
          with the master branch. Neither Gitk nor Git are capable of showing the
          commits in master.}
        \label{fig:gitk}
%\vspace{-4mm}
\end{figure*}

\begin{figure}
        \centering
        \includegraphics[width=0.45\textwidth]{figures/github_viewer.png}
        \caption{Github Failure Message showing the DAG of the Linux Project and its
                relationship to other forks.}
        \label{fig:gitfail}
%\vspace{-2mm}
\end{figure}

@@

@@

        \foreach \x in {0, 1, 2, 3, 4, 5, 6, 7, 8}
    \node[shift={(\x, -0.6)}, color=black] {$t_\x$};
  \end{tikzpicture}
  \caption{Example of a sequence of events performed in different
    repositories. The horizontal axis represents time. Each horizontal
    section represents a different branch and/or repository. Each commit
    points to its ancestor.}
  \label{fig:repoEvents}
%\vspace{-3mm}
\end{figure}

@@

    \draw (12) edge[-stealth] (11) edge[chartyellow, -stealth] (10);
    \draw (11) edge[-stealth] (4) edge[chartyellow, -stealth] (9);
    \draw (10) edge[chartyellow, -stealth] (9);
    \draw (9) edge[chartmagenta, -stealth] (8) edge[chartred, -stealth] (6)
              edge[chartyellow, -stealth] (7);
    \draw (8) edge[chartmagenta, -stealth] (7);
    \draw (7) edge[chartyellow, -stealth] (5);
    \draw (6) edge[chartred, -stealth] (5);
    \draw (5) edge[chartmagenta, -stealth] (3) edge[chartyellow,-stealth] (2)
              edge[chartyellow, -stealth] (4);
    \draw (4) edge[-stealth] (1);
    \draw (3) edge[chartmagenta, -stealth] (2);
    \draw (2) edge[chartyellow, -stealth] (1);
  \end{tikzpicture}
  \caption{DAG representation of the commits represented in
    Figure~\ref{fig:repoEvents}. The DAG loses information about which
    repository the commit is performed in and through which merges it
    has passed on its way to the master branch. The DAG does not even
    distinguish the master branch from other branches.}
  \label{fig:repoDAG}
%\vspace{-3mm}
\end{figure}

@@

  \end{tikzpicture}
  \caption{Merge-tree view of the commits  represented in
    Figure~\ref{fig:repoEvents} showing the path they followed to reach
    the master branch. In this model the successors of each commit
    represents the path followed by that commit to reach the master
    branch.}
  \label{fig:repoTree}
\vspace{-3mm}
\end{figure}

@@

\begin{algorithm}
        \caption{Computing the merge-tree of Linux Git's DAG}\label{fig:alg}
        \begin{algorithmic}
                \Function{ComputeMergeTree}{DAG}: tree
                \State {\# Compute the tree from the DAG of Linux repository.}
                \State {\# Returns $Tree$, a graph containing every commit }
                \State {\# in DAG with the path it followed to master.}

@@

* 'for-linus' of git://neil.brown.name/md: (24 commits)
md: clean up do_md_stop
[... edited for the sake of space]
md: split out md_rdev_init
md: be more careful setting MD_CHANGE_CLEAN
md/raid5: ensure we create a unique name for kmem_cache...
...
        \end{verbatim}}\vspace{-5mm}
        \caption{Example of how merges record a subset of commits being merged. The
                commit only shows the first 20 one-line summaries messages for the 24
                non-merge commits it merged. The ending ``...'' is part of the log
                and represents that other commits were merged.}
        \label{fig:sampleMerge}
\end{figure}

We used this information to evaluate the accuracy of the merge-tree model extracted from the DAG. The method we followed
started with the extraction of the commit history up to July 20, 2016. We computed the merge tree of every commit until
then. Since Linus Torvalds mostly does merging directly into master, we assumed that every merge by him is the root of a
merge-tree. As described above, the log of a commit usually contains the number of commits in the merge the first 20
summaries of commits being merged. We extracted merges by Linus Torvalds using the command \mycode{log --merges --author='Torvalds} and compared
the number of commits in according to the log with the number of commits in the  merge-tree rooted in this commit. We
also used the summaries of the commits found in the merge (not necessarily all---see above) to make sure those 
commits were in their corresponding merge tree. For example, for the merge in Figure~\ref{sampleMerge} we would expect
that the merge tree rooted at \mycode{8cbd84f} contains 24 commits, and the one-line summaries corresponds to commits in
that merge-tree. We also inspected those with differences to make sure they were true errors.

The results can be summarized as follows:

\begin{itemize}
\item 5 merges were false-erros because their logs did not contain accurate information (were probably edited by
  hand). For example in \mycode{42a579a0f...}) one commit summary was missing (the line was empty), in another  \mycode
  {c55d267}) the summaries were reordered.
\item The heuristic works correctly for all merges except between Jun 7, 2014 and Jun 2, 2014 (92 merges) and before
  Sept 4, 2007. Before this date merges did not include a summary of the commits they included, hence making it
  impossible to verify; however, we correctly identified the merges by Linus into master. 
\item Before Dec. 12, 2006 (1542 merges) our heuristic breaks due to the
presence of \textit{foxtrot} commits, which confound the true master branch of a
repository
\footnote{See \url{http://bit-booster.blogspot.ca/2016/02/no-foxtrots-allowed.html} for a description of the issue}, and
is not capable of identifying most of the merges before this date.
\end{itemize}

Of the merges after Sept 4, 2007, in 99.4\% fo them (16,768 out of 16,860)  our heuristic was correct. Overall, we
correctly identified the merge trees of 87.15\% of the merges into master in Linux.

The verification detected no incorrect merges since 2013, two incorrect merges in
2012, and two in 2011; however, the heuristic breaks in October, 15, 2009
